---
theme-settings:
  theme: default
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"
  footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_default)'

survey-settings:
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  all-questions-required: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
---

```{r}
library(surveydown)
```

--- welcome

# Default Template

Welcome to surveydown! This is a default template of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "What's your favorite penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```

You don't need to insert navigation buttons with `sd_nav()` on each page, as the buttons will appear automatically by default. But you can add `sd_nav()` to override navigation defaults, like specifying the page to go to next with the `page_next` argument set to the name of the page you want to go to next, or `show_prev = FALSE` to hide the Previous button.

```{r}
sd_nav(page_next = 'page2', show_prev = FALSE)
```

--- page2

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)
```

--- end

## End

This is the last page in the survey.

```{r}
sd_close()
```
