---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: default
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_default)'

# Survey Settings
use-cookies: false
auto-scroll: false
rate-survey: false
system-language: en
highlight-unanswered: true
highlight-color: blue
capture-metadata: true
all-questions-required: false
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# Default Template

Welcome to surveydown! This is a default template of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "What's your favorite penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```

You need to insert navigation buttons with `sd_nav()` on each page. By default, it will go to the next page defined in the `survey.qmd` file, but you can also specify the page with the `next_page` argument set to the name of the page you want to go to next. Use `show_prev = FALSE` on the first page to hide the Previous button.

```{r}
sd_nav(next_page = 'page2', show_prev = FALSE)
```

:::

::: {.sd_page id=page2}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)

sd_nav()
```

:::

::: {.sd_page id=end}

## End

This is the last page in the survey.

```{r}
sd_close()
```

:::
