---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

## surveydown

<!-- badges: start -->
[![CRAN
status](https://www.r-pkg.org/badges/version/surveydown)](https://CRAN.R-project.org/package=surveydown)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/surveydown)](https://cran.r-project.org/package=surveydown)
<!-- badges: end -->

> Note: This site only documents the {surveydown} R package - visit our main site at [surveydown.org](https://surveydown.org) for more information!

## What is surveydown?

```{r child="man/rmdchunks/concept.Rmd"}
```

## Why surveydown?

```{r child="man/rmdchunks/motivation.Rmd"}
```

## Installation

### Install R & Quarto

```{r child="man/rmdchunks/install_R_Quarto.Rmd"}
```

### Install the {surveydown} R package

```{r child="man/rmdchunks/install_surveydown.Rmd"}
```

## Roadmap

```{r child="man/rmdchunks/todo.Rmd"}
```

## License

See the [License](https://github.com/surveydown-dev/surveydown/blob/master/LICENSE.md).

## Citation 

If you use this package for in a publication, please cite it! You can get the citation by running `citation("surveydown")` in your R console:

```{r}
#| eval: false
 
citation("surveydown")
```
