---
format:
  html:
    section-divs: false
server: shiny
include-before-body: hide_pages.js
execute:
  echo: false
theme: surveydown.scss
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

source('functions.R')
useShinyjs(rmd = TRUE)
```

::: {#welcome .sd-page}

# Welcome to my survey!

Here is a question to get started.

This question showcases what a "multiple choice" question looks like, which is created using `type = 'mc'` inside the `sd_question()` function.

It also is an example of the `show_if` feature (conditional display). If you choose the "Other" option, a second question pops up below asking to specify which other type of penguin is your favorite.

```{r}
sd_question(
  name  = 'penguins',
  type  = 'mc',
  label = "Which is your favorite type of penguin?",
  width = '100%',
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  name  = "penguins_other",
  type  = "text",
  label = "Please specify the other penguin type:"
)
```

<br>

```{r}
sd_next(next_page = 'skipif')
```

:::

::: {#skipif .sd-page}

# skip_if

This page showcases the `skip_if` feature, which allows you to skip forward in the survey based on different conditions. Depending on your choice, you'll go to a different page in the survey when you press the "Next" button.

```{r}
sd_question(
  name   = 'skip_to_page',
  type   = 'mc',
  width  = '100%',
  label  = "Where do you want to skip to?",
  option = c(
    'Take me to the page on Question Types (the next page)' = 'question_types',
    'Take me to the page on Question Formatting' = 'question_formatting',
    'Skip to the end' = 'end'
  )
)
```

<br>

```{r}
sd_next(next_page = 'questionTypes')
```

:::

::: {#questionTypes .sd-page}

# Question types

This page showcases some other question types.

#### Use `type = 'text'` to specify a text input type question:

```{r}
sd_question(
  name  = "silly_word",
  type  = "text",
  label = "Write a silly word:"
)
```

#### Use `type = 'textarea'` to specify a textarea input type question:

```{r}
sd_question(
  name  = "silly_paragraph",
  type  = "textarea",
  label = "Write a silly paragraph:"
)
```

#### Use `type = 'numeric'` to specify a numeric input type:

```{r}
sd_question(
  name  = 'age',
  type  = 'numeric',
  label = "What's your age?"
)
```

#### Use `type = 'mc'` to specify a multiple choice type question with a single choice option:

```{r}
sd_question(
  name   = 'artist',
  type   = 'mc',
  label  = "Which artist do you prefer most from this list?",
  option = c(
    "Taylor Swift" = "taylor_swift",
    "Beyoncé"      = "beyonce",
    "Adele"        = "adele",
    "Rihanna"      = "rihanna",
    "Lady Gaga"    = "ladygaga",
    "Ed Sheeran"   = "ed_sheeran",
    "Drake"        = "drake"
  )
)
```

#### Use `type = 'mc_buttons'` to generate the button version of `mc`:

```{r}
sd_question(
  name   = 'fruit',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Use `type = 'mc_multiple'` to specify a multiple choice type question with multiple selection enabled:

```{r}
sd_question(
  name   = 'swift',
  type   = 'mc_multiple',
  label  = "Which are your favorite Taylor Swift albums (select all that apply)?",
  option = c(
    "Taylor Swift (2006)" = "taylor_swift",
    "Fearless (2008)"     = "fearless",
    "Speak Now (2010)"    = "speak_now",
    "Red (2012)"          = "red",
    "1989 (2014)"         = "1989",
    "Reputation (2017)"   = "reputation",
    "Lover (2019)"        = "lover",
    "Folklore (2020)"     = "folklore",
    "Evermore (2020)"     = "evermore",
    "Midnights (2022)"    = "midnights"
  )
)
```

#### Use `type = 'mc_multiple_buttons'` to generate the button version of `mc_multiple`:

```{r}
sd_question(
  name  = 'michael_jackson',
  type  = 'mc_multiple_buttons',
  label = "Which are your favorite Michael Jackson songs (select all that apply)?",
  option = c(
    "Thriller (1982)"          = "thriller",
    "Billie Jean (1982)"       = "billie_jean",
    "Beat It (1982)"           = "beat_it",
    "Man in the Mirror (1987)" = "man_in_the_mirror",
    "Smooth Criminal (1987)"   = "smooth_criminal",
    "Black or White (1991)"    = "black_or_white",
    "Bad (1987)"               = "bad",
    "Human Nature (1982)"      = "human_nature"
  )
)
```

#### Use `type = 'select'` to specify a drop down select type question:

```{r}
sd_question(
  name   = 'education',
  type   = 'select',
  label  = "What is the highest level of education you have attained?",
  option = c(
    "Did not attend high school" = "hs_no",
    "Some high school"           = "hs_some",
    "High school graduate"       = "hs_grad",
    "Some college"               = "college_some",
    "College"                    = "college_grad",
    "Graduate Work"              = "grad",
    "Prefer not to say"          = "no_response"
  )
)
```

#### Use `type = 'slider'` to specify a slider input type:

```{r}
sd_question(
  name  = 'climate_care',
  type  = 'slider',
  label = "To what extent do you believe human-caused climate change is real?",
  option = c(
    "Don't Believe"    = "dont_believe",
    "Somewhat Believe" = "somewhat",
    "Neutral"          = "neutral",
    "Believe"          = "believe",
    "Strongly Believe" = "strongly_believe"
  )
)
```

#### `type = 'slider'` can also be used to select a range:

```{r}
sd_question(
  name     = 'coldest_months',
  type     = 'slider',
  label    = "What months do you think are the coldest throughout a year?",
  option   = month.abb,
  selected = month.abb[c(4, 8)]
)
```

#### Use `type = 'date'` to specify a date input type:

```{r}
sd_question(
  name  = 'dob',
  type  = 'date',
  label = "What is your date of birth?"
)
```

#### Use `type = 'daterange'` to specify a daterange input type:

```{r}
sd_question(
  name  = 'hs_date',
  type  = 'daterange',
  label = "When did you start and finish high school?"
)
```

<br>

```{r}
sd_next(next_page = 'questionFormatting')
```

:::

::: {#questionFormatting .sd-page}

# Question formatting

On this page, we'll demonstrate some of the formatting options for displaying questions.

<br>

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

## Thanks for taking our survey!

:::

```{r}
#| context: server

config <- sd_config(
  db_key = "", 
  db_url = "",
  skip_if = tibble::tribble(
    ~question_id,  ~question_value, ~target,
    "skip_to_page", "end",           "end", 
    "skip_to_page", "question_formatting",  "questionFormatting"
  ),
  show_if = tibble::tribble(
    ~question_id,  ~question_value, ~target,
    "penguins",    "other",         "penguins_other",
  )
)

sd_server(
  input   = input,
  session = session,
  config  = config
)
```
