---
format:
  html:
    section-divs: false
server: shiny
include-before-body: hide_pages.js
execute:
  echo: false
theme: surveydown.scss
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

source('functions.R')
useShinyjs(rmd = TRUE)
```

::: {#welcome .sd-page}

# Welcome to my survey! 

Here is a question to get started. If you choose the Blue pill, you'll skip to the end. If you choose the Red pill, you'll see the rest of the pages.

```{r}
sd_question(
  name     = 'color',
  type     = 'mc',
  required = TRUE,
  label    = "Do you want to take the red pill or the blue pill?",
  option   = c(
    'Blue' = 'blue', 
    'Red' = 'red'
  )
)
```

Here is a question to showcase conditional display logic. If you choose "Yes" to the question below, another question will appear below it:

```{r}
sd_question(
  name = "have_pet",
  type = "mc",
  label = "Do you have a pet?",
  option = c(
    "No" = "no",
    "Yes" = "yes"
  )
)

sd_question(
  name = "pet_name",
  type = "text",
  label = "What's your pet's name?"
)

sd_next(current_page = 'welcome')
```

:::

::: {#demographics .sd-page}

## Tell us abour yourself!

```{r}
sd_question(
  name     = 'age',
  type     = 'numeric',
  required = TRUE,
  label    = "What's your age?",
  option   = NULL
)

sd_question(
  name     = 'gender',
  type     = 'mc',
  required = TRUE,
  label    = "Which best describes your gender?",
  option   = c(
    "Female" = "female",
    "Male" = "male",
    "Prefer not to say" = "opt_out"
  )
)

sd_question(
  name     = 'ethnicity',
  type     = 'mc_multiple',
  required = TRUE,
  label    = "Which best describes your ethnicity (select all that apply)?",
  option   = c(
    "Asian" = "asian",
    "Black/African" = "black",
    "White" = "white",
    "Hispanic/Latinx" = "hispanic",
    "Native American" = "native",
    "Pacific Islander" = "pacific",
    "Prefer not to say" = "opt_out"
  )
)

sd_next(current_page = 'demographics')
```

:::

::: {#animals .sd-page}

## Here are a few more questions to finish up!

```{r}
sd_question(
  name     = 'animal',
  type     = 'text',
  required = FALSE,
  label    = "What's your favorite animal?"
)

sd_question(
  name     = 'education',
  type     = 'select',
  required = TRUE,
  label    = "What is the highest level of education you have attained?",
  option   = c(
    "Did not attend high school" = "hs_no",
    "Some high school"           = "hs_some",
    "High school graduate"       = "hs_grad",
    "Some college"               = "college_some",
    "College"                    = "college_grad",
    "Graduate Work"              = "grad",
    "Prefer not to say"          = "no_response"
  )
)

sd_next(current_page = 'animals')
```

:::

::: {#end .sd-page}

## Thanks for taking our survey!

:::

```{r}
#| context: server

sd_server(
  input = input,
  session = session,
  skip_if = list(
    list(
      condition = function(input) input$color == 'blue', 
      target_page = 'end'
    )
  ),
  show_if = list(
    list(
      condition = function(input) input$have_pet == 'yes', 
      dependent_question = 'have_pet',
      target_question = 'pet_name'
    )
  )
)
```
