---
format:
  html:
    section-divs: false
server: shiny
include-before-body: hide_pages.js
execute:
  echo: false
theme: surveydown.scss
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

source('functions.R')
useShinyjs(rmd = TRUE)
```

::: {#welcome .sd-page}
# Welcome to my survey!

Here is a question to get started.

This question showcases what a "multiple choice" question looks like, which is created using `type = 'mc'` inside the `sd_question()` function.

It also is an example of the `show_if` feature (conditional display). If you choose the "Other" option, a second question pops up below asking to specify which other type of penguin is your favorite.

```{r}
sd_question(
  name   = 'penguins',
  type   = 'mc',
  label  = "**Which is your favorite type of penguin?**",
  width = '100%',
  option = c(
    'Adélie' = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo' = 'gentoo',
    'Other' = 'other'
  )
)

sd_question(
  name  = "penguins_other",
  type  = "text",
  label = "**Please specify the other penguin type:**"
)
```

<br>

```{r}
sd_next(next_page = 'skipif')
```

:::

::: {#skipif .sd-page}
# skip_if

This page showcases the `skip_if` feature, which allows you to skip forward in the survey based on different conditions. Depending on your choice, you'll go to a different page in the survey when you press the "Next" button.

```{r}
sd_question(
  name     = 'skip_to_end',
  type     = 'mc',
  required = TRUE,
  width = '100%',
  label    = "**Where do you want to skip to?**",
  option   = c(
    'Take me to the page on Question Types (the next page)' = 'question_types',
    'Skip to the end' = 'end'
  )
)
```

<br>

```{r}
sd_next(next_page = 'questionTypes')
```


:::

::: {#questionTypes .sd-page}
# Question types

This page showcases some other question types.

#### Use `type = 'text'` to specify a text input type question:

```{r}
sd_question(
  name  = "silly_word",
  type  = "text",
  label = "**Write a silly word:**",
  width = '60%'
)
```

#### Use `type = 'numeric'` to specify a numeric input type:

```{r}
sd_question(
  name     = 'age',
  type     = 'numeric',
  required = TRUE,
  label    = "**What's your age?**",
  option   = NULL,
  width = '60%'
)
```

#### Use `type = 'mc'` to specify a multiple choice type question with a single choice option:

```{r}
sd_question(
  name     = 'artist',
  type     = 'mc',
  required = TRUE,
  width = '100%',
  label    = "**Which artist do you prefer most from this list?**",
  option   = c(
    "Taylor Swift" = "taylor_swift",
    "Beyoncé"      = "beyonce",
    "Adele"        = "adele",
    "Rihanna"      = "rihanna",
    "Lady Gaga"    = "ladygaga",
    "Ed Sheeran"   = "ed_sheeran",
    "Drake"        = "drake"
  )
)
```

#### Use `type = 'mc_buttons'` to generate the button version of `mc`:

```{r}
sd_question(
  name     = 'fruit',
  type     = 'mc_buttons',
  required = TRUE,
  label    = "**Which fruit do you prefer most from this list?**",
  width = '100%',
  option   = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Use `type = 'mc_multiple'` to specify a multiple choice type question with multiple selection enabled:

```{r}
sd_question(
  name     = 'swift',
  type     = 'mc_multiple',
  required = TRUE,
  width = '100%',
  label    = "**Which are your favorite Taylor Swift albums (select all that apply)?**",
  option   = c(
    "Taylor Swift (2006)" = "taylor_swift",
    "Fearless (2008)"     = "fearless",
    "Speak Now (2010)"    = "speak_now",
    "Red (2012)"          = "red",
    "1989 (2014)"         = "1989",
    "Reputation (2017)"   = "reputation",
    "Lover (2019)"        = "lover",
    "Folklore (2020)"     = "folklore",
    "Evermore (2020)"     = "evermore",
    "Midnights (2022)"    = "midnights"
  )
)
```

#### Use `type = 'mc_multiple_buttons'` to generate the button version of `mc_multiple`:

```{r}
sd_question(
  name     = 'michael_jackson',
  type     = 'mc_multiple_buttons',
  individual = TRUE,
  required = TRUE,
  width = '100%',
  label    = "**Which are your favorite Michael Jackson songs (select all that apply)?**",
  option   = c(
    "Thriller (1982)"          = "thriller",
    "Billie Jean (1982)"       = "billie_jean",
    "Beat It (1982)"           = "beat_it",
    "Man in the Mirror (1987)" = "man_in_the_mirror",
    "Smooth Criminal (1987)"   = "smooth_criminal",
    "Black or White (1991)"    = "black_or_white",
    "Bad (1987)"               = "bad",
    "Human Nature (1982)"      = "human_nature"
  )
)
```

#### Use `type = 'select'` to specify a drop down select type question:

```{r}
sd_question(
  name     = 'education',
  type     = 'select',
  required = TRUE,
  width = '60%',
  label    = "**What is the highest level of education you have attained?**",
  option   = c(
    "Did not attend high school" = "hs_no",
    "Some high school"           = "hs_some",
    "High school graduate"       = "hs_grad",
    "Some college"               = "college_some",
    "College"                    = "college_grad",
    "Graduate Work"              = "grad",
    "Prefer not to say"          = "no_response"
  )
)
```

<br>

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}
## Thanks for taking our survey!
:::

```{r}
#| context: server

sd_server(
  input = input,
  session = session,
  skip_if = tibble::tribble(
    ~question_id,  ~question_value, ~target,
    "skip_to_end", "end",           "end"
  ),
  show_if = tibble::tribble(
    ~question_id,  ~question_value, ~target,
    "penguins",    "other",         "penguins_other",
  )
)
```
