---
title: "Basic Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

## Introduction

The `surveydown` R package works together with the `surveydown` Quarto extension. As a simplification, we call them together as "`surveydown`" in this article.

`surveydown` is a handy tool for survey construction, release, and data collection. It is constructed using [Quarto](https://quarto.org). Its UI is supported by the [Shiny](https://www.rstudio.com/products/shiny/) server and its database is served by [Supabase](https://supabase.com). With `surveydown`, you can create HTML survey pages by constructing a Quarto doc with extension of `qmd`.

[Quarto](https://quarto.org) is a revolutionary publication tool. A Quarto doc accepts markdown texts, R scripts, Python scripts, and more. [Shiny](https://www.rstudio.com/products/shiny/) is an R web app development platform, but in `surveydown`, we only utilized its server. [Supabase](https://supabase.com) is an open-source database supplier that delivers input-output services and exports our survey results. For more information about their basic usage, please proceed to their official websites.

### Why Use `surveydown`

There are already plenty of mature survey platforms, including Google Form, Prolific, Dynata, etc., so how is surveydown different? The primary reason is that it is R language supported

## Preparation

`surveydown` works with Quarto. Make sure you have the latest version of [Quarto](https://quarto.org) installed. Quarto works best with [RStudio](https://www.rstudio.com/categories/rstudio-ide/), but you can also have it on [VS Code](https://code.visualstudio.com) or [Positron](https://github.com/posit-dev/positron) (a novel IDE made by Posit), so please install Quarto together with any IDE of your preference.

**(Instructions here for installing `surveydown`)**

## Basic Use

Our HTML survey page is constructed using a `.qmd` file (aka a Quarto Doc file). This file consists of **4 parts: a YAML header, a setup code chunk, the survey body, and a server code chunk in the end**. Please see explanation below.

### 1. The YAML Header

YAML (Yet Another Markup Language) is an essential part for all `.qmd` files. It regulates the basic settings, including page layout, themes, add-on `css` or `js` files, etc., of your HTML page. These settings are called **keys**.

Below are the **essential** YAML scripts for the surveydown project. It contains two keys: `server`, and `filters`.

``` yaml
---
server: shiny
filters: [surveydown]
---
```

The `server: shiny` key designates the Shiny server to our page, and `filters: [surveydown]` applies the surveydown Quarto extension.

Below are the **optional** YAML scripts that you may use:

``` yaml
---
theme: united # Any bootswatch theme or a customized scss file
barcolor: theme # "theme" (default) or a customized hex code
barposition: top # "top" (default), "bottom", or "none" 
---
```

There are [25 bootswatch themes](https://bootswatch.com) to choose from. You can also use our customized `scss` theme file, or even combine these two. An example combination is shown below:

``` yaml
---
theme: [united, custom.scss]
---
```

It means to use the [united bootswatch theme](https://bootswatch.com/united/), and overwrite with the `custom.scss` file. For example, if you don't like the orange primary color of this theme, you can define `$primary` as something else in your own `scss` file. We've prepared a `custom.scss` file in our [surveydown demo repo](https://github.com/jhelvy/surveydown_demo) on GitHub.

The `barcolor` key defines the color of the progress bar. It's default to "`theme`", meaning it will reflect any primary color that the theme defines. You may also use any hex codes to overwrite this color as you wish.

The `barposition` key defines the position of the progress bar. It's default to "`top`", meaning the bar will be on the top of the page. You can change to "`bottom`" or "`none`".

You may define other YAML scripts if you want to further customize the layout of your HTML page.

### 2. The Setup Code Chunk

After the YAML header, you'll need to load the `surveydown` package and run the `sd_setup()` function:

```{r eval=FALSE}
library(surveydown)
sd_setup()
```

### 3. The Survey Body

Now you are ready to start writing your survey contents. You can write markdown texts for explanations and instructions, and insert R code chunks to present survey questions.

Here is a question to get started.

This question showcases what a "multiple choice" question looks like, which is created using `type = 'mc'` inside the `sd_question()` function.

It also is an example of the `show_if` feature (conditional display). If you choose the "Other" option, a second question pops up below asking to specify which other type of penguin is your favorite. This is controlled with the `show_if` argument to the `sd_config()` function defined in the server section at the bottom of the `.qmd` file.

```{r eval=FALSE}
# A multiple choice question with an "Other" option
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    
    # This "Other" option triggers the "penguins_other" question
    'Other'     = 'other'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_other",
  label = "Please specify the other penguin type:"
)
```

### 4. 
