---
title: "Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

# Install R

It kind of goes without saying, but you need to [install R](https://cloud.r-project.org/) for this R package to work.

# Install Quarto

{surveydown} works with [Quarto](https://quarto.org), so make sure you have the [latest version installed](https://quarto.org/docs/get-started/).

Also, Quarto works great with an IDE. We recommend [RStudio](https://www.rstudio.com/categories/rstudio-ide/), but you can also use it with [VS Code](https://code.visualstudio.com) or [Positron](https://github.com/posit-dev/positron) (a novel IDE made by Posit).

# Install the package

For now, {surveydown} is not get on CRAN, but you can install the development version from [GitHub](https://github.com/jhelvy/surveydown) by running the following command in R:

```{r}
#| eval: false

# install.packages("remotes")
remotes::install_github("jhelvy/surveydown")
```

# Quarto extension

Finally, the {surveydown} package works in tandem with our [surveydown Quarto extension](https://github.com/jhelvy/surveydown-ext), which is required to make everything work. The extension is needed in the root directory folder of every survey project you create, so don't worry about installing it now - just know that you'll need it eventually.
