---
title: "Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

# Install R & Quarto

You need both: 

- [Install R](https://CRAN.R-project.org/)
- [Install Quarto](https://quarto.org/docs/get-started/)

Also, we recommend working with an IDE. [RStudio](https://www.rstudio.com/categories/rstudio-ide/) is great, and we also like [VS Code](https://code.visualstudio.com) and [Positron](https://github.com/posit-dev/positron).

# Install the {surveydown} R package

{surveydown} is not yet on CRAN, but you can install the development version from GitHub with the following command in R:

```{r}
# install.packages("remotes")
remotes::install_github("jhelvy/surveydown")
```

# Install the surveydown Quarto Extension

Once you start working on an actual survey, you'll need the [surveydown Quarto extension](https://github.com/jhelvy/surveydown-ext). We recommend starting with a template survey, which will automatically add the latest extension for you:

```{r}
surveydown::sd_create_survey("path/to/folder")
```

Otherwise, you can install the extension using the *terminal* or with the {surveydown} package:

- Using the *Terminal*:

```
quarto install extension jhelvy/surveydown-ext
```

- Using the {surveydown} R package:

```{r}
surveydown::sd_update_extension()
```

# Version Control

To check if you have the latest R package and Quarto extension versions installed, run:

```{r}
surveydown::sd_check_versions()
```

To update the R package and Quarto extension to the latest version:

```{r}
surveydown::sd_update_surveydown()
```
