---
title: "2. Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{2. Installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

# Install R

It kind of goes without saying, but you need to [install R](https://cloud.r-project.org/).

# Install Quarto

{surveydown} works with [Quarto](https://quarto.org), so make sure you have the [latest version installed](https://quarto.org/docs/get-started/).

Also, Quarto works great with an IDE. We recommend [RStudio](https://www.rstudio.com/categories/rstudio-ide/), but you can also use it with [VS Code](https://code.visualstudio.com) or [Positron](https://github.com/posit-dev/positron).

# Install the {surveydown} R package

{surveydown} is not yet on CRAN, but you can install the development version from [GitHub](https://github.com/jhelvy/surveydown) by running the following command in R:

```{r}
# install.packages("remotes")
remotes::install_github("jhelvy/surveydown")
```

# Install the surveydown Quarto Extension

Every {surveydown} survey requires the [surveydown Quarto extension](https://github.com/jhelvy/surveydown-ext) to work. Unlike the {surveydown} R package (which is installed globally), **the extension must be locally installed** in the `_extensions` folder in your survey project folder. 

The latest extension will be automatically installed if you start with a template survey with `surveydown::sd_create_survey("path/to/folder")`. Otherwise, you can install the extension using the *terminal* or with the {surveydown} package:

1. Using the *Terminal*:

```
quarto install extension jhelvy/surveydown-ext
```

2. Using the {surveydown} R package:

```{r}
surveydown::sd_update_extension()
```

# Version Control

To check if you have the latest R package and Quarto extension versions installed, run:

```{r}
surveydown::sd_check_versions()
```

To update the R package and Quarto extension to the latest version:

```{r}
surveydown::sd_update_surveydown()
```
