---
title: "Setting a Password"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting a Password}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

> Every surveydown survey needs a password to secure access to the survey data. You should set one password for each project.

# What is the password used for?

Your password is used for two purposes:

1. Obtaining access to the admin page of your survey (see [admin](../articles/config.html#admin-page)).
2. Obtaining access to the Supabase database storing your survey data (ee `vignette("database")`).

# How do I set a password?

To set your surveydown password in this project, run:

```{r}
sd_set_password("your_password")
```

> Warning: Do **NOT** put the `sd_set_password()` function in your .qmd file!

This is designed to be run once in your R console and not again (unless you want to change the password).

# What does it do?

By running `sd_set_password()`, a `.Renviron` file is created in your project directory that contains your password. This file is used to access your database and write data to it, as well as provide access to the admin page. It must remain in the root project directory.

The call to `sd_set_password()` also adds a .gitignore file in your project with `.Renviron` in it, so it won't be accidentally uploaded to github. If a .gitignore file already exists, it will be updated to include `.Renviron`).
