---
title: "1. Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

> This is a tl;dr page that gives you the basic idea of how to use surveydown.

# Installation

To install the {surveydown} **R package** (not available on CRAN yet):

```{r}
#| eval: false
 
# install.packages("remotes")
remotes::install_github("jhelvy/surveydown")
```

To install the surveydown **Quarto extension**, your can either do so using the *Terminal*, or using the {surveydown} *R package*:

1. Using *Terminal* (next to the "Console" panel in your RStudio), run:

```
# Make sure you have Quarto installed.
quarto install extension jhelvy/surveydown-ext
```

2. Using the {surveydown} *R package*, run:

```{r}
#| eval: false

# Make sure you have the {surveydown} R package installed.
surveydown::sd_update_extension()
```

# Start from Exmaple Survey

To start with an **example survey** (which includes the extension), run:

```{r}
#| eval: false

# To install the survey under your current path
surveydown::sd_create_survey()

# To designate a path inside your current path
surveydown::sd_create_survey("path/to/folder")
```

# Version Control

To check if the R package and Quarto extension versions are up to date, run:

```{r}
#| eval: false

surveydown::sd_check_versions()
```

To update the R package and Quarto extension to the latest version, run:

```{r}
#| eval: false

surveydown::sd_update_surveydown()
```
