---
title: "Introduction to surveydown"
description: >
  Learn how to get started with the basics of surveydown.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to surveydown}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

In surveydown, your entire survey is designed using markdown and R code in a single Quarto document (a `.qmd` file). The {surveydown} R package provides a set of functions for defining the survey content and control logic. Each function starts with `sd_` to make them easy to identify.

You can add content to your survey using markdown formatting, or in RStudio you can edit with the visual editor. Survey questions are defined in R code chunks with the `sd_question()` function. Pages are defined using fences (`:::`), and navigation buttons handled with the `sd_next()` function. You can modify the control logic in the server code chunk (the last code chunk at the bottom of the .qmd file) with the `sd_config()` function, and you can configure the database with the `sd_database()`. Details on each of these steps are provided in separate guides in the documentation.

This introduction covers the basic steps to get started with surveydown.

# 1. Install surveydown

See `vignette("install")`

# 2. Start with a template

In the R console, run the following to to setup a template survey:

```{r}
surveydown::sd_create_survey("path/to/folder")
```

This will create a folder located at `"path/to/folder"` with the following files:

- `example.qmd`: a template survey you should edit.
- `example.Rproj`: An RStudio project file (helpful if you're working in RStudio)
- `_extensions`: A folder with the [surveydown Quarto extension](https://github.com/jhelvy/surveydown-ext) needed to make everything work (don't modify this).

# 3. **Add content**

See `vignette("content")` for details on adding content to your survey, like text, images, etc. with markdown and / or code chunks. As a quick overview:

- Add pages using fences, like this:

```
::: {#page1 .sd-page}

Page 1 content here

:::
```

- Add questions with the `sd_question()` function in code chunks (see `vignette("questions")` for supported question types). For example:

````
`r ''````{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```
````

# 4. **Add control logic**

In the server chunk (bottom of qmd file), add control logic to your survey with the `sd_config()` function. See `vignette("control")`

# 5. **Setup your database**

Also in the server chunk, setup your database with the `sd_database()` function, or leave it blank to preview / edit your survey without database connected. See `vignette("database")`

# 6. **Locally preview**

Preview your survey by clicking the "Run Document" button in RStudio or in your terminal running the command `quarto serve survey_file_name.qmd`.

# 7. **Deploy**

Deploy your survey by hosting it on your favorite server, like shinyapps.io, huggingface, etc. See `vignette("deploy")`
