---
name: "surveydown demo"
author: "John Paul Helveston"
output:
  surveydown::survey:
    css:
      - default
    lib_dir: libs
questions: questions.yml
control:
  welcome
  screener
  skip:
    condition: age > 40
    distination: end_screen
  other
  end
  stop
  end_sreen
  stop
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

library(surveydown)
```

name: welcome

# Welcome!

This is a demo survey! Click the button below to go to the next page.

---

name: screener

This is a screener.

You must choose "Red" in the question below, otherwise you will be screened out (meaning you will be sent to the end of the survey)

```{r}
q(
  name     = 'color',
  type     = 'mc',
  required = TRUE,
  label    = "Do you want to take the red pill or the blue pill?",
  option   = c('Red', 'Blue')
)
```

---

name: other

Here are some more questions:

```{r}
q(
  name     = 'age',
  type     = 'numeric',
  required = TRUE,
  label    = "What's your age?",
  option   = 25
)
```

{{ question gender }}

{{ question gender_self_describe }}

{{ question education }}

{{ question rexper }}

---

name: end

# Fine

Thank you for taking our survey!

---

name: end_screenout

Sorry, but you do not qualify to continue in the survey.
