---
server: shiny
filters: [surveydown]
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

# Run this in your Terminal to install the Quarto extension:
# quarto install extension jhelvy/surveydown-ext

# Run this in your Console to install the R package:
# remotes::install_github("jhelvy/surveydown", force = TRUE)

# Load the package locally:
# devtools::load_all("../surveydown")

# Load the package from library:
library(surveydown)

# Load other necessary packages:
library(tidyverse)
library(glue)

# This is essential to the survey:
sd_setup()
```

::: {#welcome .sd-page}

# Welcome to our survey!

This is a simple demonstration of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question, created using `type = 'mc'` inside the `sd_question()` function:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which type of penguin do you like the best?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```

<br>

You need to insert next buttons with `sd_next()` and set the `next_page` argument to the name of the page you want to go to next.

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)
```
 
<br>

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

This it the last page in the survey

:::

```{r}
#| context: server

# surveydown stores data on a database that you define at https://supabase.com/
# To connect to a database to store the survey data, update this with details
# from your supabase account and database. See documentation for details.
# For security, we recommend storing your supabase password in your R
# environment instead of hard-coding it here, which you can open and edit with
# usethis::edit_r_environ()

 db <- sd_database(
   host       = NULL,
   db_name    = NULL,
   port       = NULL,
   user       = NULL,
   table_name = NULL,
   password   = Sys.getenv("SUPABASE_PASSWORD")
 )

# If you don't have a database setup you can just leave the function blank.

db <- sd_database()

# Use the sd_config() function to customize features in your survey, like
# logic to conditionally display questions or skip to pages based on
# responses to skip other questions in your survey. See documentation for
# details. For this simple survey, we'll just leave this function blank.

config <- sd_config()

# The sd_server function initiates your survey - don't change this

sd_server(
  input   = input,
  session = session,
  config  = config,
  db      = db
)
```
