---
echo: false
warning: false
---

```{r}
library(surveydown)
library(sortsurvey)
```

::: {#welcome .sd-page}

# Welcome to our survey!

This is a simple demonstration of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question, created using `type = 'mc'` inside the `sd_question()` function:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which type of penguin do you like the best?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)

sd_question(
  type  = 'rank_list',
  id    = 'penguins_drag',
  label = "Which type of penguin do you like the best? Rank them from best to worst.",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)



```

# Bucket list style:

```{r}

# add in drag and drop question
# horizontal method doesn't seem to work regardless of what width/height is
# set to

# DOES NOT WORK: input id is only set for bucket top class, 
# need to set two other input IDs for rank_list objects

# see function bucket_list_survey in sortsurvey https://github.com/saudiwin/sortable_survey/blob/main/R/bucket_list.R
# and add_rank_list in sortable: https://rstudio.github.io/sortable/reference/add_rank_list.html

sd_question(
  type  = 'bucket_list',
  id    = 'penguins_bucket',
  label = "Which type of penguin do you like the best? Drag those penguins to the second bucket.",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
    
)


```


You need to insert next buttons with `sd_next()` and set the `next_page` argument to the name of the page you want to go to next.

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)

sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

## End

This it the last page in the survey.

```{r}
sd_close("Exit Survey")
```

:::
