---
server: shiny
filters: [surveydown]
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

library(surveydown)

# Initial setup function (required)
sd_setup()
```

::: {#welcome .sd-page}

# Welcome to my survey!

Here is a question to get started.

This question showcases what a "multiple choice" question looks like, which is created using `type = 'mc'` inside the `sd_question()` function.

It also is an example of the `show_if` feature (conditional display). If you choose the "Other" option, a second question pops up below asking to specify which other type of penguin is your favorite. This is controlled with the `show_if` argument to the `sd_config()` function defined in the server section at the bottom of the .qmd file.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_other",
  label = "Please specify the other penguin type:"
)
```

<br>

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)
```
 
<br>

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

This it the last page in the survey

:::

```{r}
#| context: server

# To connect to a database to store the survey data, update this:
# db <- sd_database(
#   host = "",
#   db_name = "",
#   port = "",
#   user = "",
#   table_name = "Table1",
#   password   = Sys.getenv("SUPABASE_PASSWORD")
# )

config <- sd_config(
  # Use this function to customize features, like skip logic inside the survey.
)

sd_server(
  input   = input,
  session = session,
  config  = config
  # db      = db
)
```
