---
name: "surveydown demo"
author: "John Paul Helveston"
output: html_document
---

<!--   surveydown::survey: -->
<!--     css: -->
<!--       - default -->
<!--     lib_dir: libs -->
<!--     control: -->
<!--       skip: -->
<!--         condition: color == "Blue" -->
<!--         destination: end_screenout -->
<!--       stop: end -->
<!--       stop: end_screenout -->
<!-- --- -->

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

library(surveydown)
```

name: welcome

# Welcome!

This is a demo survey! Click the button below to go to the next page.

---

name: screener

This is a screener.

You must choose "Red" in the question below, otherwise you will be screened out (meaning you will be sent to the end of the survey)

```{r}
question(
  name     = 'color',
  type     = 'mc',
  required = TRUE,
  label    = "Do you want to take the red pill or the blue pill?",
  option   = c('Red', 'Blue')
)
```

---

name: other

Here are some more questions:

```{r}
question(
  name     = 'age',
  type     = 'numeric',
  required = TRUE,
  label    = "What's your age?",
  option   = NULL
)

question(
  name     = 'gender',
  type     = 'mc',
  required = TRUE,
  label    = "Which best describes your gender?",
  option   = c(
    female = "Female",
    male = "Male",
    opt_out = "Prefer not to say",
    self_desc = "Prefer to self describe"
  )
)

question(
  name     = 'gender_self_describe',
  type     = 'text',
  required = FALSE,
  label    = "Which best describes your gender?",
  dependence = 'gender',
  dependence_value = "Prefer to self describe"
)

question(
  name     = 'education',
  type     = 'select',
  required = TRUE,
  label    = "What is the highest level of education you have attained?",
  option   = c(
    hs_no        = "Did not attend high school",
    hs_some      =  "Some high school",
    hs_grad      = "High school graduate",
    college_some = "Some college",
    college_grad = "College",
    grad         = "Graduate Work",
    no_response  = "Prefer not to say"
  )
)

question(
  name     = 'rexper',
  type     = 'mc',
  required = TRUE,
  label    = "Have you ever learned to program in R?",
  option   = c(yes = "Yes", no = "No")
)
```

---

name: end

# Fine

Thank you for taking our survey!

---

name: end_screenout

Sorry, but you do not qualify to continue in the survey.
