```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

> This is a tl;dr of how to make a survey with surveydown.

### 1. [**Install surveydown**]()

### 2. **Start with a template**

```{r, child='template.Rmd'}
```

### 3. **Add content**

Add text, images, etc. with markdown and / or code chunks, and insert [questions]() with the `sd_question()` function in code chunks.

### 4. **Add control logic**

In the server chunk (bottom of qmd file), add [control logic]() to your survey by modifying the `sd_config()` function.

### 5. **Setup your database**

Also in the server chunk, [setup your database]() by modifying the `sd_database()` function, or leave it blank to preview / edit your survey without your database connected.

### 6. **Locally preview**

Preview your survey by clicking the "Run Document" button in RStudio or in your terminal running the command `quarto serve survey_file_name.qmd`.

### 7. **Deploy** 

[Deploy your survey] by hosting it on your favorite server, like shinyapps.io, huggingface, etc.
