---
survey-settings:
  show-previous: true
---

```{r}
library(surveydown)
```

--- page1

# Navigation Example with sd_nav()

This is the first page of the survey. Notice the navigation button only shows "Next" because we set `show_prev = FALSE`.

```{r}
sd_question(
  type  = 'text',
  id    = 'name',
  label = 'What is your name?'
)

sd_nav(show_prev = FALSE)
```

--- page2

This is the second page. Now both "Previous" and "Next" buttons are shown.

```{r}
sd_question(
  type  = 'mc',
  id    = 'color',
  label = "What's your favorite color?",
  option = c(
    'Red'    = 'red',
    'Blue'   = 'blue',
    'Green'  = 'green'
  )
)
```

--- page3

This is the third page. You can customize button labels if needed.

```{r}
sd_question(
  type  = 'text',
  id    = 'feedback',
  label = 'Any feedback?'
)

sd_nav(
  prev_label = "Go Back",
  next_label = "Continue"
)
```

--- end

## Survey Complete!

You've reached the end of the survey. Notice how you can navigate back to any previous page using the "Previous" button.

```{r}
sd_close()
```
