```{r}
library(surveydown)
```

--- initial_page

# Fruit Selection

Please select your favorite fruit.

```{r}
sd_question(
  type   = 'mc',
  id     = 'fav_fruit',
  label  = 'What is your favorite fruit?',
  option = c(
    'Apple'  = 'apple',
    'Orange' = 'orange',
    'Other'  = 'other'
  )
)
```

--- default_page

# Default Next Page

This is the default next page that appears if no skip conditions are met.

```{r}
sd_question(
  type   = 'text',
  id     = 'default_text',
  label  = 'This is the default page. We did not expect to see you here!'
)
```

--- apple_page

# Apple Page

You selected Apple as your favorite fruit.

```{r}
sd_question(
  type   = 'text',
  id     = 'apple_text',
  label  = 'Tell us something about apples:'
)

sd_nav(page_next = "summary_page")
```

--- orange_page

# Orange Page

You selected Orange as your favorite fruit.

```{r}
sd_question(
  type   = 'text',
  id     = 'orange_text',
  label  = 'Tell us something about oranges:'
)

sd_nav(page_next = "summary_page")
```

--- other_page

# Other Fruit Page

You selected Other as your favorite fruit.

```{r}
sd_question(
  type   = 'text',
  id     = 'other_text',
  label  = 'What is your favorite fruit and why?'
)

sd_nav(page_next = "summary_page")
```

--- summary_page

# Survey Summary

Thank you for completing our fruit survey!

```{r}
sd_close("Exit Survey")
```
